State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-01-28 draft.tex
Had forgotten one change.
what happened

[ticket: X]
Change in proof of thm 14.
what happened

[ticket: X]

%% Ticket list
\openTickets{Manuel:wlog,Manuel:convHull,Manuel:remConcavity,Manuel:thm14:ref,Manuel:invertability:assumption,Manuel:inclusion:step,Manuel:minus:one}

@@

% \textcolor{red}{
Given $\mathcal{R}_{k-1} = \{ x : \xi_{i,k-1} x \leq 1 \ \forall i \in \mathcal{I}_{k-1}\}$, we can compute $\mathcal{R}_k$ using (\ref{eq:Rk:iteration}) and (\ref{eq:definition:PWA:polytopic:set:vertices}) as
\begin{subequations}\label{eq:Rk:explicit}
\begin{gather}
\mathcal{R}_k = \Bigl\{ x : \xi_{i,k-1} x + \zeta_{i,k-1}(x) \leq 1 \ \forall i \in \mathcal{I}_{k-1} \Bigr\} \\
\zeta_{i,k-1}(x) = \max_{j} \xi_{i,k-1} \Psi^{k-1} v_j(\Psi^{-k}x) ,
\end{gather}
\end{subequations}
and the approach outlined in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ without explicitly determining $\zeta_{i,k-1}(x)$ for all $x\in\mathcal{R}_{k-1}$. This gives $\mathcal{X}_k = \mathcal{X}_{k-1}\cap \{x: \xi_{i,k}\Psi^k x \leq 1\, \forall i \in \mathcal{I}_k\}$,%
% }
%
% Using (\ref{eq:Rk:iteration})-(\ref{eq:definition:PWA:polytopic:set:vertices}), the set $\mathcal{D}_k$ can be expressed 
% \begin{subequations}\label{eq:explicit:Dk}
% \begin{gather}
% \mathcal{D}_k = \Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \zeta_{i,l}(x) \leq 1 \ \forall i \in \mathcal{I}_{\mathcal{X}}\Bigr\} \\
% \zeta_{i,l}(x) = \max_{j} \xi_i \Psi^l v_j(x) ,
% \end{gather}
% \end{subequations}
% %Clearly $\mathcal{X}_k$ is a convex polyhedral set for each finite $k$, 
% and the approach described in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{X}_k = \{x: \xi_{i,k} x \leq 1,\, \forall i \in \mathcal{I}_k\}$ for each $k=0,1,\ldots$ without explicitly determining $\zeta_{i,k}(x)$ for all $x\in\mathcal{X}_{k-1}$. 
%
and the implied iteration is summarized as follows.
%
\begin{alg}(Computation of MRPI set $\mathcal{X}^\infty$)\label{alg:MRPI:set}\\
\textsc{Data}: 
\begin{tabular}[t]{@{}l@{}}
$\Psi$, 
$\mathcal X= \{x: \xi_i x \leq 1 \, \forall i\in\mathcal{I}_{\mathcal{X}}\}$, 
and\\
$\mathcal{V}(x) = \conv\{\Theta_j x + \theta_j,\, j\in\mathbb{N}_q\}$.
\end{tabular}
\\
\textsc{Initialization}:
$\mathcal{X}_0 \gets \mathcal{X}$, 
% \textcolor{red}{
$\mathcal{R}_0 \gets \mathcal{X}$
% }
, $k\gets 1$.\\
% \begin{tabular}[t]{@{}l@{}}
% $\mathcal{X}_0 \gets \mathcal{X}$, 
% \textcolor{red}{$\mathcal{I}_0\gets \mathcal{I}_{\mathcal{X}}$, 
% $\xi_{i,0}\gets \xi_i\, \forall i\in\mathcal{I}_0$}\\
% \textcolor{red}{$k\gets 1$.}\end{tabular}\\
\begin{tabular}{@{}l@{~}l@{}}
1. &
% \textcolor{red}{%
Compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ using (\ref{eq:Rk:explicit}a,b)%
% }
\\ 
& 
% \textcolor{red}{%
and 
$\mathcal{D}_k \gets \Psi^{-k}\mathcal{R}_k$.%
% }
\\
% $\begin{aligned}[t]\mathcal{D}_k\gets 
% \displaystyle\Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \xi_{i}\Psi^l(\Theta_j x &+ \theta_j)
% \leq 1 \\ 
% &\forall i \in \mathcal{I}_{\mathcal{X}}, \, \forall j\in\mathbb{N}_q \Bigr\};\end{aligned}$\\
2. &
\begin{tabular}[t]{@{}l@{}}
If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then\\ \hspace{2em}$\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop;\end{tabular}\\
& 
\begin{tabular}[t]{@{}l@{}}
else\\
\hspace{2em}$\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1; \end{tabular}\\
& end
% 2. &
% If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then $\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop.\\
% & 
% Else
% $\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1.
\end{tabular}
\end{alg}

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k = \mathcal{X}_{k-1} \cap D_l$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \left\{ n , \left\lceil \frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rceil \todo{Manuel:minus:one}{- 1} \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%

>>>>

%% Ticket list
\openTickets{Manuel:wlog,Manuel:convHull,Manuel:remConcavity,Manuel:thm14:ref,Manuel:invertability:assumption,Manuel:inclusion:step,Manuel:minus:one,Manuel:proof:thm14}

@@

% \textcolor{red}{
Given $\mathcal{R}_{k-1} = \{ x : \xi_{i,k-1} x \leq 1 \ \forall i \in \mathcal{I}_{k-1}\}$, we can compute $\mathcal{R}_k$ using (\ref{eq:Rk:iteration}) and (\ref{eq:definition:PWA:polytopic:set:vertices}) as
\begin{subequations}\label{eq:Rk:explicit}
\begin{gather}
\mathcal{R}_k = \Bigl\{ x : \xi_{i,k-1} x + \zeta_{i,k-1}(x) \leq 1 \ \forall i \in \mathcal{I}_{k-1} \Bigr\} \\
\zeta_{i,k-1}(x) = \max_{j} \xi_{i,k-1} \Psi^{k-1} v_j(\Psi^{-k}x) ,
\end{gather}
\end{subequations}
and the approach outlined in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ without explicitly determining $\zeta_{i,k-1}(x)$ for all $x\in\mathcal{R}_{k-1}$. This gives $\mathcal{X}_k = \mathcal{X}_{k-1}\cap \{x: \xi_{i,k}\Psi^k x \leq 1\, \forall i \in \mathcal{I}_k\}$,%
% }
%
% Using (\ref{eq:Rk:iteration})-(\ref{eq:definition:PWA:polytopic:set:vertices}), the set $\mathcal{D}_k$ can be expressed 
% \begin{subequations}\label{eq:explicit:Dk}
% \begin{gather}
% \mathcal{D}_k = \Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \zeta_{i,l}(x) \leq 1 \ \forall i \in \mathcal{I}_{\mathcal{X}}\Bigr\} \\
% \zeta_{i,l}(x) = \max_{j} \xi_i \Psi^l v_j(x) ,
% \end{gather}
% \end{subequations}
% %Clearly $\mathcal{X}_k$ is a convex polyhedral set for each finite $k$, 
% and the approach described in Remark~\ref{rem:pPdiff:calculation} can be used to compute $\mathcal{X}_k = \{x: \xi_{i,k} x \leq 1,\, \forall i \in \mathcal{I}_k\}$ for each $k=0,1,\ldots$ without explicitly determining $\zeta_{i,k}(x)$ for all $x\in\mathcal{X}_{k-1}$. 
%
and the implied iteration is summarized as follows.
%
\begin{alg}(Computation of MRPI set $\mathcal{X}^\infty$)\label{alg:MRPI:set}\\
\textsc{Data}: 
\begin{tabular}[t]{@{}l@{}}
$\Psi$, 
$\mathcal X= \{x: \xi_i x \leq 1 \, \forall i\in\mathcal{I}_{\mathcal{X}}\}$, 
and\\
$\mathcal{V}(x) = \conv\{\todo{Manuel:convHull}{\max_k}\Theta_{j\todo{Manuel:convHull}{,k}} x + \theta_{j\todo{Manuel:convHull}{,k}},\, j\in\mathbb{N}_q\}$.
\end{tabular}
\\
\textsc{Initialization}:
$\mathcal{X}_0 \gets \mathcal{X}$, 
% \textcolor{red}{
$\mathcal{R}_0 \gets \mathcal{X}$
% }
, $k\gets 1$.\\
% \begin{tabular}[t]{@{}l@{}}
% $\mathcal{X}_0 \gets \mathcal{X}$, 
% \textcolor{red}{$\mathcal{I}_0\gets \mathcal{I}_{\mathcal{X}}$, 
% $\xi_{i,0}\gets \xi_i\, \forall i\in\mathcal{I}_0$}\\
% \textcolor{red}{$k\gets 1$.}\end{tabular}\\
\begin{tabular}{@{}l@{~}l@{}}
1. &
% \textcolor{red}{%
Compute $\mathcal{R}_k = \{x: \xi_{i,k} x \leq 1\, \forall i \in \mathcal{I}_k\}$ using (\ref{eq:Rk:explicit}a,b)%
% }
\\ 
& 
% \textcolor{red}{%
and 
$\mathcal{D}_k \gets \Psi^{-k}\mathcal{R}_k$.%
% }
\\
% $\begin{aligned}[t]\mathcal{D}_k\gets 
% \displaystyle\Bigl\{x : \xi_i \Psi^k x + \sum_{l=0}^{k-1} \xi_{i}\Psi^l(\Theta_j x &+ \theta_j)
% \leq 1 \\ 
% &\forall i \in \mathcal{I}_{\mathcal{X}}, \, \forall j\in\mathbb{N}_q \Bigr\};\end{aligned}$\\
2. &
\begin{tabular}[t]{@{}l@{}}
If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then\\ \hspace{2em}$\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop;\end{tabular}\\
& 
\begin{tabular}[t]{@{}l@{}}
else\\
\hspace{2em}$\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1; \end{tabular}\\
& end
% 2. &
% If $\mathcal{D}_k \supseteq \mathcal{X}_{k-1}$, then $\mathcal{X}^\infty \gets \mathcal{X}_{k-1}$; stop.\\
% & 
% Else
% $\mathcal{X}_k \gets \mathcal{D}_k \cap \mathcal{X}_{k-1}$; reduce$(\mathcal{X}_k)$; $k\gets k+1$; go to 1.
\end{tabular}
\end{alg}

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k \todo{Manuel:proof:thm14}{\supseteq} \mathcal{X}_{k-1} \cap D_k$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \left\{ n , \left\lceil \frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rceil \todo{Manuel:minus:one}{- 1} \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%
